%%
%% This is file `bath-bst-v1.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% bath_bst.dtx  (with options: `tex1')
%% ----------------------------------------------------------------
%% bath-bst --- Harvard referencing style as recommended by the University of Bath Library
%% Author:  Alex Ball
%% E-mail:  a.j.ball@bath.ac.uk
%% License: Released under the LaTeX Project Public License v1.3c or later
%% See:     http://www.latex-project.org/lppl.txt
%% ----------------------------------------------------------------
%% 
\ProvidesFile{bath-bst-v1.tex}
    [2022/05/25 v6.0 Harvard referencing style as recommended by the University of Bath Library]

\documentclass[10pt,a4paper]{article}
\usepackage[british]{babel}
\usepackage[hmargin=3cm,vmargin=2.5cm]{geometry}
\frenchspacing


\usepackage{iftex}
\ifPDFTeX
  \usepackage{CJKutf8}
\else
  \ifLuaTeX
    \usepackage{luatexja-fontspec}
    \setmainjfont{IPAexGothic}
  \else
    \ifXeTeX
    \usepackage{ctex}
    \fi
  \fi
\fi


\usepackage{xpatch,csquotes,xcolor,xparse,multicol,fancyvrb}
\xdefinecolor{Green}{rgb}{0,.5,0}
\xdefinecolor{Slate}{RGB}{80,86,94}
\xdefinecolor{BathStone}{RGB}{213,211,185}
\xdefinecolor{SlushPuppy}{RGB}{177,215,237}
\colorlet{ok}{Green}
\colorlet{todo}{red}
\colorlet{hacked}{orange}
\colorlet{manual}{purple}
\RecustomVerbatimEnvironment
  {Verbatim}{Verbatim}
  {commentchar=\%}

\usepackage[tightLists=false]{markdown}
\markdownSetup{rendererPrototypes={%
    link = {\href{#3}{#1}}%
}}

\usepackage{fontawesome}[2015/07/07]
\newcommand{\booksym}{\makebox[1em][c]{\faicon{book}}}
\newcommand{\cogsym}{\makebox[1em][c]{\faicon{cog}}}
\makeatletter
\newcommand{\hangfrom}[1]{%
  \setbox\@tempboxa\hbox{{#1}}%
  \hangindent \wd\@tempboxa\noindent\box\@tempboxa}
\makeatother
\newenvironment{tips}{%
  \begin{list}{\makebox[2em][c]{\faLightbulbO}}{%
    \setlength{\leftmargin}{2em}
    \setlength{\labelwidth}{2em}
    \setlength{\labelsep}{0pt}}
}{\end{list}}
\newenvironment{info}{%
  \begin{list}{\makebox[2em][c]{\faInfoCircle}}{%
    \setlength{\leftmargin}{2em}
    \setlength{\labelwidth}{2em}
    \setlength{\labelsep}{0pt}}
}{\end{list}}
\newenvironment{hacks}{%
  \begin{list}{\makebox[2em][c]{\faWrench}}{%
    \setlength{\leftmargin}{2em}
    \setlength{\labelwidth}{2em}
    \setlength{\labelsep}{0pt}}
}{\end{list}}

\usepackage{tcolorbox}
\tcbuselibrary{listings,breakable,skins,xparse}
\colorlet{Option}{violet}
\newcommand*{\key}[1]{\textcolor{Option}{\ttfamily #1}}
\lstdefinelanguage{bafll}%
  { alsoletter={.}
  , morekeywords=[2]%
    { add.period$
    , call.type$
    , change.case$
    , chr.to.int$
    , cite$
    , duplicate$
    , empty$
    , format.name$
    , global.max$
    , if$
    , int.to.chr$
    , int.to.str$
    , missing$
    , newline$
    , num.names$
    , pop$
    , preamble$
    , purify$
    , quote$
    , skip$
    , sort.key$
    , stack$
    , substring$
    , swap$
    , text.length$
    , text.prefix$
    , top$
    , type$
    , warning$
    , while$
    , width$
    , write$
    }
  , morekeywords=[3]%
    { ENTRY
    , INTEGERS
    , STRINGS
    , MACRO
    , FUNCTION
    , READ
    , EXECUTE
    , ITERATE
    , SORT
    , REVERSE
    }
  , morekeywords=[1]{}
  , otherkeywords=%
    { +
    , -
    , >
    , <
    , =
    , *
    , :=
    }
  , sensitive=true
  , morestring=[b]"
  , morecomment=[l]\%
  }[keywords,strings,comments]
\lstloadlanguages{[LaTeX]TeX,bafll}
\lstdefinestyle{dtxlatex}%
  { columns=fullflexible
  , basicstyle=\ttfamily
  , language={[LaTeX]TeX}
  , texcsstyle=*\color{red!75!black}
  , commentstyle=\color{gray}\itshape
  , moretexcs=
    { citet
    , citep
    , defcitealias
    , citepalias
    , citetalias
    , noop
    , urlprefix
    , urldateprefix
    }
  , moredelim=**[s][\color{violet}]{[}{]}
  , moredelim=**[s][\color{blue!75!black}]{\{}{\}}
  }
\lstdefinestyle{dtxbst}%
  { columns=fullflexible
  , basicstyle=\ttfamily
  , language=bafll
  , keywordstyle=[1]\color{orange!75!black}
  , keywordstyle=[2]\color{red!75!black}
  , keywordstyle=[3]\color{green!50!black}
  , commentstyle=\color{gray}\itshape
  , stringstyle=\color{violet}
  , mathescape=false
  , showstringspaces=false
  }
\lstset{style=dtxlatex}
\tcbset
  { colframe = Slate
  , colback = BathStone!25
  , listing options =
    { style = tcblatex
    , style = dtxlatex
    , basicstyle=\ttfamily\small
    }
  }
\NewTColorBox{bibexbox}{D(){ok}d<>m}%
  {bicolor
  ,colframe = #1
  ,colback = #1!5!white
  ,colbacklower = white
  ,fontlower = \footnotesize
  ,before upper = {\hangfrom{\booksym\space}}
  ,after upper = {\par\hangfrom{\cogsym\space}\bibentry{#3}.}
  ,IfNoValueTF={#2}{}%
    {overlay = {
      \node[anchor=south east,text=teal] at (frame.south east) {#2};
      }
    }
  }
\def\bstIonly{\tcbset{colback=hacked!10}}
\def\bstIIonly{\tcbset{colback=SlushPuppy!25}}
\def\bstboth{\tcbset{colback=BathStone!25}}


\usepackage{natbib}
\setlength{\bibhang}{0pt}
\newcommand*{\urlprefix}{Available from: }
\newcommand*{\urldateprefix}{Accessed }

\usepackage{bibentry}
\bibliographystyle{bath}
\nobibliography*

\usepackage{readprov}
\usepackage[british,cleanlook]{isodate}

\usepackage[colorlinks,citecolor=black]{hyperref}
\makeatletter
\Urlmuskip=0mu plus 3mu\relax
\mathchardef\UrlBigBreakPenalty=100\relax
\mathchardef\UrlBreakPenalty=200\relax
\def\UrlBigBreaks{\do\:\do\-}%
\def\UrlBreaks{%
  \do\.\do\@\do\/\do\\\do\!\do\_\do\|\do\;\do\>\do\]\do\)\do\}%
  \do\,\do\?\do\'\do\+\do\=\do\#\do\$\do\&\do\*\do\^\do\"}%
\let\do=\noexpand
\makeatother

\sloppy

\title{bath-bst: Harvard referencing style as recommended by the University of Bath Library}
\author{%
  Maintainer: Alex Ball\thanks{%
    To contact the maintainer about this package, please visit the repository
    where the code is hosted: \url{https://github.com/alex-ball/bathbib}.%
  }%
}
\date{Package \UseVersionOf{\jobname.tex} --\printdateTeX{\UseDateOf{\jobname.tex}}}

\begin{document}
\maketitle

\section{Introduction}


The data model offered by the standard Bib\TeX\ styles, and even the extended
\textsf{natbib} variants, is not really rich enough to support the nuances of
the Harvard (Bath) style. This means design decisions have to be made about
whether to attempt some level of compatibility with other styles or craft
something utterly unique.

In the first version of \textsf{bath-bst}, the intention was to set things up
so that, if the same \texttt{.bib} file was used with a different style, the features
peculiar to the Harvard (Bath) style would be ignored and the remaining
information would come out in a sensible arrangement. The recommendations of
the style's documentation were to use the standard entry types as much as
possible (though more semantic aliases were provided), and minimal new fields
were introduced. For the more exotic (in Bib\TeX\ terms) demands of the style,
extensive use was made of the (standard) \texttt{note} and (non-standard)
\texttt{titleaddon} fields to place information properly. If you have written
a \texttt{.bib} file according the principles in that first version, the \texttt{bath}
style will still work as advertised for you.

The second version introduced a new variant, \texttt{bathx} (`Bath extended'),
which has a different aim. The idea with this one is that \texttt{.bib} files written
for this style will be rendered just the same by the companion
\textsf{biblatex-bath} style. Where possible, features from the latter have
been emulated for Bib\TeX; otherwise, the `cheats' used in this style will
also work under \textsf{biblatex}.

Happily, it has been possible to do this while keeping most of the code in
common. The main differences between two versions are as follows:

\begin{itemize}
\item
  In \texttt{bath}, the \texttt{titleaddon} field is printed bare, while
  in \texttt{bathx} it is wrapped in square brackets.
\item
  In \texttt{bathx} online items are marked with `[Online]' automatically,
  while in \texttt{bath} you have to mark them thus yourself.
\item
  In \texttt{bathx} undated items are marked with `n.d.' automatically,
  while in \texttt{bath} you have to give `n.d.' as the value of \texttt{year}
  yourself.
\end{itemize}

One other change worth noting regards URL access dates. In version 1, the
advice was to put them in \texttt{urldate}. From version 2, the advice is
to put them, perhaps counter-intuitively, in \texttt{urlyear}. The reason is that
\textsf{biblatex} will complain if the value of \texttt{urldate} is in the wrong
format, but will happily print the contents of \texttt{urlyear} literally. If
you don't care about \textsf{biblatex} compatibility, you can continue to use
\texttt{urldate}.

This document provides a suite of examples that demonstrate and test the
\texttt{bath} bibliography style with mostly standard Bib\TeX entry types
and fields.

\section{Using the style}

To use the style, add these lines to your preamble:

\begin{tcblisting}{listing only}
\usepackage{natbib}
\newcommand*{\urlprefix}{Available from: }
\newcommand*{\urldateprefix}{Accessed }
\bibliographystyle{bath}
\end{tcblisting}

Remember also to specify your \texttt{.bib} file at the end of the document:

\begin{tcblisting}{listing only}
\bibliography{file}
\end{tcblisting}

To make a citation in the text, use the key that corresponds to the entry in your \texttt{.bib} file:

\begin{tcblisting}{}
While collections can be supplemented by other means \citep{devlin.etal2021ipp},
the absence of an invisible collection amongst historians is noted by
\citet[p.556]{stieg1981inh}. It may be, as \citet{burchard1965hhl} points out,
that they have no assistants or are reluctant to delegate, or it may be
down to economic factors \citep{adams2009tc1, adams2014tc2, gb.pa2014,
adams2017tc3}\dots
\end{tcblisting}

Please refer to the documentation for \href{http://www.ctan.org/pkg/natbib}{\textsf{natbib}}
for the full range of commands available for in-text citations. Be aware that the
\textsf{natbib} option \texttt{sort} will sort citations in bibliography order,
rather than the chronological order demanded by Harvard (Bath) -- so don't use it!

\section{Breaking changes between versions}

The following sections list implementation changes that might affect the way
in which you write your bibliography database files.

In addition to the changes listed, when upgrading between major versions,
you should expect some changes in formatting relating to the evolution of the
Harvard (Bath) style itself. Some of the style's internal settings and
structures may also change without warning.

\subsection{Version 3}

\begin{itemize}
\item
  Journal titles are now coerced to sentence case, so any capital letters you
  want to keep need to be protected with braces.
\item
  Entries of type \texttt{unpublished} are now marked as unpublished. If you
  have been using this for an item that should not be marked as unpublished
  (e.g.~archive photographs, law reports), you can use \texttt{booklet} instead:
  this is the other entry type (along with \texttt{misc}) that has a
  \texttt{howpublished} field instead of a \texttt{publisher}.
  Other entry types may work as well; indeed, some examples below have been updated to use \texttt{manual} or \texttt{report} instead.
\item
  Some changes to the Harvard (Bath) style cannot be applied automatically
  (e.g.~the update to how standards are referenced), so you may need to update
  your .bib file accordingly.
\end{itemize}

\subsection{Version 5}

\begin{itemize}
\item
  In the 2021 revision of the style, the titles of broadcast media (TV, radio)
  became upright, with series information for titled episodes being italic.
  If you have been using \texttt{booklet} for such entries, you should now use \texttt{misc} instead.
\item
  Series names (except those in \texttt{legislation} and \texttt{jurisdiction}
  entries) are now coerced to sentence case, so any capital letters you
  want to keep need to be protected with braces.
\item
  If the title is moved to the head of the reference (before the year),
  the \texttt{titleaddon} field is now printed directly after it instead of after the year.
  This supports cases where `[Online]' needs to be printed before the year,
  but may mean different workarounds are needed for other entries such as anonymous works with translated titles.
\item
  The \texttt{article} and \texttt{manual} entry types now support the \texttt{month} field.
\item
  Maps need to be given the \texttt{book} entry type; previously \texttt{manual} was recommended.
\end{itemize}

\subsection{Version 6}

\begin{itemize}
\item
  All elements of the title block (including \texttt{titleaddon},
  \texttt{version}, and \texttt{entrysubtype}) now move to the head of the
  reference in the absence of an author\slash editor.
\end{itemize}

\section{Examples}

The examples below are shown in three parts.
The first, marked with \faBook, shows an extract from the
\href{https://library.bath.ac.uk/referencing/harvard-bath}{\emph{Referencing guide: Harvard Bath}} or
\href{https://library.bath.ac.uk/images/referencing}{\emph{Referencing images}}.
The second, marked with \faCog, shows the reference as formatted by Bib\TeX.
The last shows how the reference was entered in the \texttt{.bib} file.
The bottom right corner shows the source of the example: `RX' indicates the `Reference examples (A-Z)' section of the Guide; `RL' indicates the `Organise a reference list' section of the Guide; `RI' indicates \emph{Referencing images}.

Some examples are highlighted in
\tcbox[colframe=hacked,colback=hacked!5!white,nobeforeafter,size=fbox,tcbox raise base]{orange}.
This indicates that some fields have been `abused' to achieve the right effect;
in other words, they contain information that does not conform with their intended use.
Some others make use of the \texttt{note} and \texttt{titleaddon} fields to achieve
the right effect, where other styles might need the information placed differently.
Particular care should be taken with such items when switching between different styles,
though of course any item might need adjustment to take account of differing conventions.

\subsection{Books and book chapters}

\subsubsection*{Book with author(s)}

\begin{bibexbox}<RX>{rang.etal2012rdp}
  Rang, H.P., Dale, M.M., Ritter, J.M., Flower, R.J. and Henderson, G., 2012. \emph{Rang and Dale's pharmacology}. 7th ed. Edinburgh: Elsevier Churchill Livingstone.
  \tcblower
\begin{Verbatim}
@book{rang.etal2012rdp,
  author = {Rang, H. P. and Dale, M. M. and Ritter, J. M. and Flower, R. J. and Henderson, G.},
  year = {2012},
  title = {Rang and {Dale's} Pharmacology},
  edition = {7},
  address = {Edinburgh},
  publisher = {Elsevier Churchill Livingstone}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{ou1972em}
  Open University, 1972. \emph{Electricity and magnetism}. Bletchley: Open University Press.
  \tcblower
\begin{Verbatim}
@book{ou1972em,
  author = {{Open University}},
  year = {1972},
  title = {Electricity and Magnetism},
  address = {Bletchley},
  publisher = {Open University Press}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{solomon.etal2019cbe}
  Solomon, M.R., Askegaard, S., Hogg, M. and Bamossy, G.J., 2019. \emph{Consumer behaviour: a European perspective}. 7th ed. Harlow: Pearson.
  \tcblower
\begin{Verbatim}
@book{solomon.etal2019cbe,
  author = {Solomon, M. R. and Askegaard, S. and Hogg, M. and Bamossy, G. J.},
  year = {2019},
  title = {Consumer Behaviour: a {European} Perspective},
  edition = {7},
  address = {Harlow},
  publisher = {Pearson}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Book with editor(s) instead of author(s)}

\begin{bibexbox}<RX>{rothman.etal2008me}
  Rothman, K.J., Greenland, S. and Lash, T.L., eds, 2008. \emph{Modern epidemiology}. 3rd ed. Philadelphia, Pa.: Lippincott Williams \& Wilkins.
  \tcblower
\begin{Verbatim}
@book{rothman.etal2008me,
  editor = {Kenneth J. Rothman and Sander Greenland and Timothy L. Lash},
  year = {2008},
  title = {Modern Epidemiology},
  edition = {3},
  address = {Philadelphia, Pa.},
  publisher = {Lippincott Williams \& Wilkins}}
\end{Verbatim}
\end{bibexbox}

\begin{info}\item
Internally, \texttt{collection} is an alias for \texttt{book}.
\end{info}

\subsubsection*{Electronic book}

\begin{bibexbox}<RX>{haynes2014crc}
  Haynes, W.M., ed.\@, 2014. \emph{CRC handbook of chemistry and physics} [Online]. 94th ed. Boca Raton, Fla.: CRC Press/Taylor and Francis. Available from: \url{http://www.hbcpnetbase.com} [Accessed 16 June 2016].
  \tcblower
\begin{Verbatim}
@book{haynes2014crc,
  editor = {Haynes, W. M.},
  year = {2014},
  title = {{CRC} Handbook of Chemistry and Physics},
  titleaddon = {[Online]},
  edition = {94},
  address = {Boca Raton, Fla.},
  publisher = {CRC Press/Taylor and Francis},
  url = {http://www.hbcpnetbase.com},
  urldate = {16 June 2016}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{blockley2021evs}
  Blockley, D., 2021. \emph{Engineering: a very short introduction} [Online]. Oxford: Oxford University Press. Available from: \url{https://www.amazon.co.uk/kindle} [Accessed 30 June 2021].
  \tcblower
\begin{Verbatim}
@book{blockley2021evs,
  author = {Blockley, D.},
  year = {2021},
  title = {Engineering: a Very Short Introduction},
  titleaddon = {[Online]},
  address = {Oxford},
  publisher = {Oxford University Press},
  url = {https://www.amazon.co.uk/kindle},
  urldate = {30 June 2021}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Book known by its title}

\begin{info}\item
Unfortunately, to avoid breaking other use cases for the \texttt{book} entry
type, to achieve the following format you must use the non-standard
\texttt{reference} entry type.
\end{info}

\begin{bibexbox}<RX>{bnf2020}
  British National Formulary, 2020. 79th ed. London: Pharmaceutical Press.
  \tcblower
\begin{Verbatim}
@reference{bnf2020,
  year = {2020},
  title = {{British National Formulary}},
  edition = {79},
  address = {London},
  publisher = {Pharmaceutical Press}}
\end{Verbatim}
\end{bibexbox}

\begin{info}\item
Similarly, to achieve the following formats you must use the non-standard
\texttt{inreference} entry type.
\end{info}

\begin{bibexbox}<RX>{aspirin2020bnf}
  British National Formulary, 2020. 79th ed. \emph{Aspirin}. London: Pharmaceutical Press.
  \tcblower
\begin{Verbatim}
@inreference{aspirin2020bnf,
  title = {Aspirin},
  year = {2020},
  booktitle = {{British National Formulary}},
  edition = {79},
  address = {London},
  publisher = {Pharmaceutical Press}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{aspirin2019bnf}
  British National Formulary, 2019. \emph{Aspirin} [Online]. London: Pharmaceutical Press. Available from: \url{https://www.medicinescomplete.com/#/content/bnf/_456850132} [Accessed 26 November 2019].
  \tcblower
\begin{Verbatim}
@inreference{aspirin2019bnf,
  title = {Aspirin},
  titleaddon = {[Online]},
  year = {2019},
  booktitle = {{British National Formulary}},
  address = {London},
  publisher = {Pharmaceutical Press},
  url = {https://www.medicinescomplete.com/\#/content/bnf/_456850132},
  urldate = {26 November 2019}}
\end{Verbatim}
\end{bibexbox}

\begin{info}
\item
Internally, \texttt{inreference} is an alias for \texttt{incollection}.
\item
The style ensures the \texttt{booktitle} is used in title citation commands.
\end{info}

\begin{tcblisting}{}
  \cite{aspirin2019bnf}, \citet{bnf2020}, \citet{aspirin2020bnf}.
\end{tcblisting}

\subsubsection*{Chapter\slash paper from a collection (by different authors) in an edited book}

\begin{bibexbox}<RL>{burchard1965hhl}
  Burchard, J.E., 1965. How humanists use a library. In: C.F.J. Overhage and J.R. Harman, eds. \emph{Intrex: report on a planning conference and information transfer experiments}. Cambridge, Mass.: MIT Press, pp.41--87.
  \tcblower
\begin{Verbatim}
@incollection{burchard1965hhl,
  author = {Burchard, J. E.},
  year = {1965},
  title = {How Humanists use a Library},
  editor = {C. F. J. Overhage and J. R. Harman},
  booktitle = {Intrex: report on a planning conference and information transfer experiments},
  address = {Cambridge, Mass.},
  publisher = {MIT Press},
  pages = {41-87}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{reid1967ptp}
  Reid, D.R., 1967. Physical testing of polymer films. In: S.H. Pinner, ed. \emph{Modern packaging films}. London: Butterworths, pp.143--183.
  \tcblower
\begin{Verbatim}
@incollection{reid1967ptp,
  author = {D. R. Reid},
  year = {1967},
  title = {Physical Testing of Polymer Films},
  editor = {S. H. Pinner},
  booktitle = {Modern Packaging Films},
  address = {London},
  publisher = {Butterworths},
  pages = {143-183}}
\end{Verbatim}
\end{bibexbox}

\subsection{Articles and periodicals}

\subsubsection*{Journal article}

\begin{bibexbox}<RL>{stieg1981cer}
  Stieg, M.F., 1981a. Continuing education and the reference librarian in the academic and research library. \emph{Library journal}, 105(22), pp.2547--2551.
  \tcblower
\begin{Verbatim}
@article{stieg1981cer,
  author = {Stieg, M. F.},
  year = {1981},
  title = {Continuing Education and the Reference Librarian in the Academic and Research Library},
  journal = {Library Journal},
  volume = {105},
  number ={22},
  pages = {2547-2551}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RL>{stieg1981inh}
  Stieg, M.F., 1981b. The information needs of historians. \emph{College and research libraries}, 42(6), pp.549--560.
  \tcblower
\begin{Verbatim}
@article{stieg1981inh,
  author = {Stieg, M. F.},
  year = {1981},
  title = {The Information Needs of Historians},
  journal = {College and Research Libraries},
  volume = {42},
  number ={6},
  pages = {549-560}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{newman2010mcb}
  Newman, R., 2010. Malaria control beyond 2010. \emph{Brit. Med. J.}, 341(7765), pp.157--208.
  \tcblower
\begin{Verbatim}
@article{newman2010mcb,
  author = {Newman, R.},
  year = {2010},
  title = {Malaria control beyond 2010},
  journal = {{Brit.\@ Med.\@ J.}},
  volume = {341},
  number = {7765},
  pages = {157-208}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{wetzstein.etal2020iai}
  Wetzstein, G., Ozcan, A., Gigan, S., Fan, S., Englund, D., Soljacic, M., Denz, C., Miller, D.A.B. and Psaltis, D., 2020. Inference in artificial intelligence with deep optics and photonics. \emph{Nature}, 588(7836), pp.39--47.
  \tcblower
\begin{Verbatim}
@article{wetzstein.etal2020iai,
  author = {Wetzstein, G. and Ozcan, A. and Gigan, S. and Fan, S. and
    Englund, D. and Soljacic, M. and Denz, C. and Miller, D. A. B. and
    Psaltis, D.},
  year = {2020},
  title = {Inference in Artificial Intelligence with Deep Optics and Photonics},
  journal = {Nature},
  volume = {588},
  number = {7836},
  pages = {39-47}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Electronic journal article}

\begin{bibexbox}<RX>{devlin.etal2021ipp}
  Devlin, S.M., Martin, A. and Ostrovnaya, I., 2021. Identifying prognostic pairwise relationships among bacterial species in microbiome studies. \emph{PLOS Computational Biology} [Online], 17(11). Available from: \url{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1009501} [Accessed 9 December 2021].
  \tcblower
\begin{Verbatim}
@article{devlin.etal2021ipp,
  author = {Devlin, S. M. and Martin, A. and Ostrovnaya, I.},
  year = {2021},
  title = {Identifying Prognostic Pairwise Relationships Among Bacterial
    Species in Microbiome Studies},
  journal = {{PLOS Computational Biology} \textup{[Online]}},
  volume = {17},
  number = {11},
  url = {https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1009501},
  urldate = {9 December 2021}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{steward.etal2020eys}
  Steward, S., Connelly, D. and Robinson, J., 2020. Everything you should know about the coronavirus outbreak. \emph{The pharmaceutical journal} [Online]. Available from: \url{https://www.pharmaceutical-journal.com/news-and-analysis/features/everything-you-should-know-about-the-coronavirus-outbreak/20207629.article} [Accessed 30 April 2020].
  \tcblower
\begin{Verbatim}
@article{steward.etal2020eys,
  author = {Steward, S. and Connelly, D. and Robinson, J.},
  year = {2020},
  title = {Everything You Should Know About the Coronavirus Outbreak},
  journal = {The Pharmaceutical Journal \textup{[Online]}},
  url = {https://www.pharmaceutical-journal.com/news-and-analysis/features/everything-you-should-know-about-the-coronavirus-outbreak/20207629.article},
  urldate = {30 April 2020}}
\end{Verbatim}
\end{bibexbox}

\begin{hacks}\item
With most styles, you would put `in press' or `preprint' as the
\texttt{year} for articles that have yet to be officially published, but for
this style you need to put it in \texttt{volume}. If you would rather lose
this information when switching to a different style than have it incorrectly
placed, you can use the \texttt{pubstate} field from \textsf{biblatex}
instead. Use the keyword \texttt{inpress} for `in press' and
\texttt{inpreparation} or \texttt{submitted} (whichever is more accurate) for
`preprint'.

\begin{tcolorbox}%
  [ colframe = Slate
  , colback = white
  , fontupper = \footnotesize
  ]
  \begin{Verbatim}
  pubstate = {inpress},
  \end{Verbatim}
\end{tcolorbox}
\end{hacks}

\begin{bibexbox}(hacked)<RX>{liontou.etal2019dra}
  Liontou, C., Kontopodis, E., Oikonomidis, N., Maniotis, C., Tassopoulos, A., Tsiafoutis, I., Lazaris, E. and Koutouzis, M., 2019. Distal radial access: a review article. \emph{Cardiovascular revascularization medicine} [Online], in press. Available from: \url{https://www.sciencedirect.com/science/article/pii/S1553838919303367} [Accessed 19 June 2019].
  \tcblower
\begin{Verbatim}
@article{liontou.etal2019dra,
  author = {Liontou, C. and Kontopodis, E. and Oikonomidis, N. and Maniotis, C. and
    Tassopoulos, A. and Tsiafoutis, I. and Lazaris, E. and Koutouzis, M.},
  year = {2019},
  title = {Distal Radial Access: a Review Article},
  journal = {Cardiovascular revascularization medicine \textup{[Online]}},
  volume = {in press},
  url = {https://www.sciencedirect.com/science/article/pii/S1553838919303367},
  urldate = {19 June 2019}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Preprint or trial study in a digital repository}

\begin{bibexbox}<RX>{shah.corrick2016hsc}
  Shah, I. and Corrick, I., 2016. \emph{How should central banks respond to non-neutral inflation expectations?} Bath: University of Bath. \emph{OPUS} [Online]. Available from: \url{http://opus.bath.ac.uk} [Accessed 4 May 2016].
  \tcblower
\begin{Verbatim}
@techreport{shah.corrick2016hsc,
  author = {Shah, I. and Corrick, I.},
  year = {2016},
  title = {How should central banks respond to non-neutral inflation expectations?},
  address = {Bath},
  institution = {University of Bath},
  note = {\emph{OPUS} [Online]},
  url = {http://opus.bath.ac.uk},
  urldate = {4 May 2016}}
\end{Verbatim}
\end{bibexbox}

\begin{tips}\item
The Harvard (Bath) style treats preprints as grey literature, and so the
\texttt{techreport} entry type (or its alias \texttt{report}) is the best match
semantically.
\item
Use \texttt{note} to specify the name of the preprint repository.
If you don't want this information showing up in other Bib\TeX\ styles,
or you think you might want to switch to using \texttt{bathx.bst} later,
use the \texttt{library} field instead.
\end{tips}

\begin{bibexbox}<RX>{ganju2021sed}
  Ganju, V., 2021. \emph{A study of EnGeneIC Dream Vectors (EDV's) packaged with the chemotherapy, E-EDV-D682 given simultaneously as non-targeted EDVs carrying an immune enhancer called EDV-GC, in participants with advanced pancreatic and other cancers whose disease has progressed after one or two treatment regimes, or where other standard therapies are not appropriate}. Sydney: University of Sydney. \emph{Australian and New Zealand Clinical Trials Registry} [Online]. Available from: \url{http://www.anzctr.org.au/Trial/Registration/TrialReview.aspx?id=365258} [Accessed 29 April 2021].
  \tcblower
\begin{Verbatim}
@techreport{ganju2021sed,
  author = {Ganju, V.},
  year = {2021},
  title = {A study of {EnGeneIC} {Dream} {Vectors} {(EDV's)} packaged with the chemotherapy,
    {E-EDV-D682} given simultaneously as non-targeted {EDVs} carrying an immune enhancer
    called {EDV-GC}, in participants with advanced pancreatic and other cancers whose disease
    has progressed after one or two treatment regimes, or where other standard therapies are
    not appropriate},
  address = {Sydney},
  institution = {University of Sydney},
  note = {\emph{Australian and New Zealand Clinical Trials Registry} [Online]},
  url = {http://www.anzctr.org.au/Trial/Registration/TrialReview.aspx?id=365258},
  urldate = {29 April 2021}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Newspaper article}

\begin{hacks}\item
Give the issue's day and month as the \texttt{month} or \texttt{volume}.
\end{hacks}

\begin{bibexbox}(hacked)<RX>{haurant2004bbh}
  Haurant, S., 2004. Britain's borrowing hits £1 trillion. \emph{The Guardian}, 29 July, p.16c.
  \tcblower
\begin{Verbatim}
@article{haurant2004bbh,
  author = {Haurant, S.},
  year = {2004},
  title = {Britain's Borrowing Hits \pounds 1 Trillion},
  journal = {The {Guardian}},
  month = {{29 July}},
  pages = {16c}}
\end{Verbatim}
\end{bibexbox}


\begin{bibexbox}(hacked)<RX>{independent1992pub}
  The Independent, 1992. Picking up the bills. \emph{The Independent}, 4 June, p.28a.
  \tcblower
\begin{Verbatim}
@article{independent1992pub,
  author = {{The Independent}},
  year = {1992},
  title = {Picking Up the Bills},
  journal = {The {Independent}},
  month = {{4 June}},
  pages = {28a}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}(hacked)<RX>{cogley2020ccs}
  Cogley, M., 2020. Corporate confidence slumps to record low. \emph{The Telegraph} [Online], 4 May. Available from: \url{https://www.telegraph.co.uk/business/2020/05/03/corporate-confidence-slumps-all-time-low/} [Accessed 5 May 2020].
  \tcblower
\begin{Verbatim}
@article{cogley2020ccs,
  author = {Cogley, M.},
  year = {2020},
  title = {Corporate Confidence Slumps to Record Low},
  journal = {{The Telegraph} \textup{[Online]}},
  volume = {4 May},
  url = {https://www.telegraph.co.uk/business/2020/05/03/corporate-confidence-slumps-all-time-low/},
  urldate = {5 May 2020}}
\end{Verbatim}
\end{bibexbox}

\subsection{Conference papers}

\begin{info}\item
As in the standard Bib\TeX\ styles, \texttt{conference} is a legacy (and highly deprecated) alias for \texttt{inproceedings}.
\end{info}

\subsubsection*{Conference paper (when proceedings have a named editor)}

\begin{bibexbox}<RX>{crawford1965oim}
  Crawford, G.I., 1965. Oxygen in metals. In: J.M.A. Lenihan and S.J. Thompson, eds. \emph{Activation analysis: proceedings of a NATO Advanced Study Institute}, 2--4 August 1964, Glasgow. London: Academic Press, pp.113--118.
  \tcblower
\begin{Verbatim}
@inproceedings{crawford1965oim,
  author = {Crawford, G. I.},
  year = {1965},
  title = {Oxygen in Metals},
  editor = {J. M. A. Lenihan and S. J. Thompson},
  booktitle = {Activation Analysis: Proceedings of a {NATO} {Advanced} {Study} {Institute}},
  venue = {2--4 August 1964, Glasgow},
  address = {London},
  publisher = {Academic Press},
  pages = {113-118}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Conference paper (when proceedings have no named editor or are part of a major series)}

\begin{bibexbox}<RX>{soper1972rbc}
  Soper, D., 1972. Review of bracken control experiments with asulam. \emph{Proceedings of the 11th British Weed Control Conference}, 15--17 November 1972, Brighton. Brighton: University of Sussex, pp.24--31.
  \tcblower
\begin{Verbatim}
@inproceedings{soper1972rbc,
  author = {Soper, D.},
  year = {1972},
  title = {Review of Bracken Control Experiments with Asulam},
  booktitle = {Proceedings of the 11th {British} {Weed} {Control} {Conference}},
  venue = {15--17 November 1972, Brighton},
  address = {Brighton},
  publisher = {University of Sussex},
  pages = {24-31}}
\end{Verbatim}
\end{bibexbox}

\subsection{Grey literature}

\subsubsection*{Thesis/dissertation}

\begin{bibexbox}<RX>{burrell1973ist}
  Burrell, J.G., 1973. \emph{The importance of school tours in education}. Thesis (M.A.). Queen's University, Belfast.
  \tcblower
\begin{Verbatim}
@mastersthesis{burrell1973ist,
  author = {Burrell, J. G.},
  year = {1973},
  title = {The Importance of School Tours in Education},
  type = {Thesis ({M.A.})},
  school = {Queen's University, Belfast}}
\end{Verbatim}
\end{bibexbox}

\begin{info}\item
Internally, \texttt{thesis} is an alias for \texttt{phdthesis}.
\end{info}

\subsubsection*{Report, working paper, or research briefing}

\begin{bibexbox}<RX>{unesco1993gip}
  UNESCO, 1993. \emph{General information programme and UNISIST}\@. (PGI-93/WS/22). Paris: UNESCO.
  \tcblower
\begin{Verbatim}
@techreport{unesco1993gip,
  author = {{UNESCO}},
  year = {1993},
  title = {General Information Programme and {UNISIST}},
  address = {Paris},
  institution = {UNESCO},
  number = {PGI-93/WS/22}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{bre2007dqb}
  BRE, 2007. \emph{Designing quality buildings: a BRE guide}. (Report 497). Bracknell: BRE.
  \tcblower
\begin{Verbatim}
@techreport{bre2007dqb,
  author = {{BRE}},
  year = {2007},
  title = {Designing Quality Buildings: a {BRE} Guide},
  address = {Bracknell},
  institution = {BRE},
  type = {Report},
  number = {497}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{deneulin.dinerstein2010hms}
  Deneulin, S. and Dinerstein, A.C., 2010. \emph{Hope movements: social movements in the pursuit of human development}. (Bath papers in international development and wellbeing, no.~8). Bath: University of Bath.
  \tcblower
\begin{Verbatim}
@techreport{deneulin.dinerstein2010hms,
  author = {Deneulin, S. and Dinerstein, A. C.},
  year = {2010},
  title = {Hope Movements: Social Movements in the Pursuit of Human Development},
  address = {Bath},
  institution = {University of Bath},
  number = {Bath papers in international development and wellbeing, no.~8}}
\end{Verbatim}
\end{bibexbox}

\begin{info}\item
Internally, \texttt{report} is an alias for \texttt{techreport}.
\end{info}

\subsubsection*{Standard}

\begin{bibexbox}<RX>{bs5605:1990}
  BSI, 1990. \emph{BS 5605:1990 Recommendations for citing and referencing
  published material}. London: BSI.
  \tcblower
\begin{Verbatim}
@manual{bs5605:1990,
  author = {{BSI}},
  year = {1990},
  title = {{BS}~5605:1990 {Recommendations} for Citing and Referencing Published Material},
  address = {London},
  organization = {BSI}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{astm.d1655}
  ASTM, 2019. \emph{ASTM D1655 - 19 Standard specification for aviation
  turbine fuels}. West Conshohocken, Pa.: ASTM.
  \tcblower
\begin{Verbatim}
@manual{astm.d1655,
  author = {{ASTM}},
  year = {2019},
  title = {{ASTM~D1655} - 19 {Standard} Specification for Aviation Turbine Fuels},
  address = {West Conshohocken, Pa.},
  organization = {ASTM}}
\end{Verbatim}
\end{bibexbox}

\begin{info}\item Internally, \texttt{standard} is an alias for \texttt{manual}.\end{info}

\subsubsection*{Patent}

\begin{bibexbox}<RX>{pm1981opa}
  Phillipp Morris Inc., 1981. \emph{Optical perforating apparatus and system}. European patent application 0021165A1. 1981-01-07.
  \tcblower
\begin{Verbatim}
@manual{pm1981opa,
  author = {{Phillipp Morris Inc.}},
  year = {1981},
  title = {Optical perforating apparatus and system},
  series = {European patent application},
  number = {0021165A1. 1981-01-07}}
\end{Verbatim}
\end{bibexbox}

\begin{info}\item
Internally, \texttt{patent} is an alias for \texttt{manual}.
\end{info}

\subsubsection*{Unpublished written material and personal communications}

\begin{bibexbox}<RX>{harris2013fgr}
  Harris, G., 2013. \emph{Focus group recommendations: internal task group
  report}. Unpublished.
  \tcblower
\begin{Verbatim}
@unpublished{harris2013fgr,
  author = {Harris, G.},
  year = {2013},
  title = {Focus group recommendations: internal task group report}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{hadley2015bir}
  Hadley, S., 2015. \emph{Biomechanics: introductory reading, BM289: sport
  biomechanics}. University of Bath. Unpublished.
  \tcblower
\begin{Verbatim}
@unpublished{hadley2015bir,
  author = {Hadley, S.},
  year = {2015},
  title = {Biomechanics: introductory reading, {BM289}: sport biomechanics},
  howpublished = {University of Bath}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{thomas2015wcr}
  Thomas, D., 2015. Word count and referencing style. \emph{Frequently
  asked questions discussion board: PHYS 2011: housing studies}.
  University of Bath. Unpublished.
  \tcblower
\begin{Verbatim}
@unpublished{thomas2015wcr,
  author = {Thomas, D.},
  year = {2015},
  title = {Word count and referencing style},
  booktitle = {Frequently asked questions discussion board: {PHYS} 2011: housing studies},
  howpublished = {University of Bath}}
\end{Verbatim}
\end{bibexbox}

\subsection{Audiovisual materials}

\subsubsection*{Image}

\begin{tips}\item You would normally class images as \texttt{misc} or \texttt{unpublished}, but those entry types have particular formatting quirks in this style that don't work for images. Use \texttt{manual} or \texttt{booklet} instead. You can use \texttt{online} (an alias for \texttt{manual}) for online images.\end{tips}

\begin{bibexbox}<RI>{nasa2015nat}
   NASA, 2015. \emph{NASA astronaut Tim Kopra on Dec. 21 spacewalk} [Online]. Washington: NASA. Available from: \url{http://www.nasa.gov/image-feature/nasa-astronaut-tim-kopra-on-dec-21-spacewalk} [Accessed 7 January 2015].
  \tcblower
\begin{Verbatim}
@manual{nasa2015nat,
  author = {{NASA}},
  year = {2015},
  title = {{NASA} Astronaut {Tim} {Kopra} on {Dec.\@} 21 Spacewalk},
  titleaddon = {[Online]},
  address = {Washington},
  organization = {NASA},
  url = {http://www.nasa.gov/image-feature/nasa-astronaut-tim-kopra-on-dec-21-spacewalk},
  urldate = {7 January 2015}}
\end{Verbatim}
\end{bibexbox}

\begin{tips}\item
You can use either the \texttt{publisher} or the \texttt{organization} field to
record the source of the image.
\end{tips}

\begin{bibexbox}<RI>{iliff2006rcb}
   Iliff, D., 2006. \emph{Royal Crescent in Bath, England - July 2006} [Online]. San Francisco: Wikimedia Foundation. Available from: \url{https://commons.wikimedia.org/wiki/File:Royal_Crescent_in_Bath,_England_-_July_2006.jpg} [Accessed 7 January 2016].
  \tcblower
\begin{Verbatim}
@manual{iliff2006rcb,
  author = {D. Iliff},
  year = {2006},
  title = {{Royal} {Crescent} in {Bath,} {England} - {July} 2006},
  titleaddon = {[Online]},
  address = {San Francisco},
  organization = {Wikimedia Foundation},
  url = {https://commons.wikimedia.org/wiki/File:Royal_Crescent_in_Bath,_England_-_July_2006.jpg},
  urldate = {7 January 2016}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RI>{brbr1965gph}
  Bristol Region Building Record, 1965. \emph{Green Park House (since demolished), viewed from southwest} [Photograph]. BRBR, D/877/1. Archives \& Research Collections, University of Bath Library.
  \tcblower
\begin{Verbatim}
@manual{brbr1965gph,
  author = {{Bristol Region Building Record}},
  year = {1965},
  title = {{Green} {Park} {House} (since demolished), viewed from southwest},
  titleaddon = {[Photograph]},
  note = {BRBR, D/877/1},
  organization = {Archives \& Research Collections, University of Bath Library}}
\end{Verbatim}
\end{bibexbox}

\begin{tips}\item
If the \texttt{organization} is a publisher, put the location in \texttt{address} as normal;
if it is an archive or where the image is displayed, include the location within the \texttt{organization} field,
after the archive name and a comma.
\item
Put archival locator information (e.g.\@ box or shelf number) in the \texttt{note} field.
\end{tips}

\begin{info}\item
The \texttt{@image} entry type can be used for any visual artistic work,
including sculptures and interactive exhibits.
\end{info}

\subsubsection*{Map}

\begin{bibexbox}<RX>{andrews.dury1773wilts}
  Andrews, J. and Dury, A., 1773. \emph{Map of Wiltshire}, 1 inch to 2 miles. Devizes: Wiltshire Record Society.
  \tcblower
\begin{Verbatim}
@book{andrews.dury1773wilts,
  author = {Andrews, J. and Dury, A.},
  year = {1773},
  title = {Map of {Wiltshire}},
  series = {1 inch to 2 miles},
  address = {Devizes},
  publisher = {Wiltshire Record Society}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{os2020bath}
  Ordnance Survey, 2020. \emph{Street view map of University of Bath} [Online], 1:5000, OS VectorMap® Local. Available from: \url{https://digimap.edina.ac.uk/roam/map/os} [Accessed 30 April 2020].
  \tcblower
\begin{Verbatim}
@book{os2020bath,
  author = {{Ordnance Survey}},
  year = {2020},
  title = {Street view map of {University of Bath}},
  titleaddon = {[Online]},
  series = {1:5000, {OS VectorMap® Local}},
  url = {https://digimap.edina.ac.uk/roam/map/os},
  urldate = {30 April 2020}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{google2020harbourside}
  Google, 2020. \emph{Harbourside, Bristol} [Online], Google Maps. Available from: \url{https://www.google.co.uk/maps/place/Harbourside,+Bristol/} [Accessed 30 April 2020].
  \tcblower
\begin{Verbatim}
@book{google2020harbourside,
  author = {{Google}},
  year = {2020},
  title = {{Harbourside, Bristol}},
  titleaddon = {[Online]},
  series = {{Google Maps}},
  url = {https://www.google.co.uk/maps/place/Harbourside,+Bristol/},
  urldate = {30 April 2020}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Film, video or DVD}

\begin{bibexbox}<RX>{macbeth1948}
  \emph{Macbeth}, 1948. Film. Directed by Orson Welles. USA: Republic Pictures.
  \tcblower
\begin{Verbatim}
@booklet{macbeth1948,
  year = {1948},
  title = {Macbeth},
  howpublished = {Film. Directed by Orson Welles. USA: Republic Pictures}}
\end{Verbatim}
\end{bibexbox}

\begin{info}\item
Internally, \texttt{movie} and \texttt{video} are aliases for \texttt{booklet}.
\end{info}

\begin{bibexbox}<RX>{elephant-man1980}
  \emph{The elephant man} [Online], 1980. Film. Directed by David Lynch. USA: Brooksfilms. Available from: BBC iPlayer [Accessed 4 May 2021].
  \tcblower
\begin{Verbatim}
@booklet{elephant-man1980,
  year = {1980},
  title = {The elephant man},
  titleaddon = {[Online]},
  howpublished = {Film. Directed by David Lynch. USA: Brooksfilms},
  note = {Available from: BBC iPlayer [Accessed 4 May 2021]}}
\end{Verbatim}
\end{bibexbox}

\begin{hacks}\item
  There's no standardised way to provide a descriptor instead of a URL,
  so to get exactly the right formatting you need to put the whole
  availability statement as a \texttt{note}. If you don't mind an extra
  full stop, you could used \texttt{urldate} (or \texttt{urlyear}) as normal.
\end{hacks}

\subsubsection*{Online video\slash audio}

\begin{bibexbox}<RX>{moran2016sol}
  Moran, C., 2016. \emph{Save our libraries} [Online]. Available from: \url{https://www.youtube.com/watch?v=gKTfCz4JtVE&feature=youtu.be} [Accessed 29 April 2016].
  \tcblower
\begin{Verbatim}
@manual{moran2016sol,
  author = {Moran, C.},
  year = {2016},
  title = {Save Our Libraries},
  titleaddon = {[Online]},
  url = {https://www.youtube.com/watch?v=gKTfCz4JtVE&feature=youtu.be},
  urldate = {29 April 2016}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RI>{chakrabarti2016hac}
   Chakrabarti, V., 2016. \emph{How architecture and city planning can combat social inequality} [Online]. Available from: \url{https://www.curbed.com/2016/5/5/11593058/vishaan-chakrabarti-pau-curbed-appeal-podcast} [Accessed 28 March 2019].
  \tcblower
\begin{Verbatim}
@manual{chakrabarti2016hac,
  author = {Chakrabarti, V.},
  year = {2016},
  title = {How Architecture and City Planning Can Combat Social Inequality},
  titleaddon = {[Online]},
  url = {https://www.curbed.com/2016/5/5/11593058/vishaan-chakrabarti-pau-curbed-appeal-podcast},
  urlyear = {28 March 2019}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Television or radio broadcast}


\begin{bibexbox}<RX>{inn2021huw}
  Hurry up and wait, 2021. \emph{Inside no.9}, \emph{Episode 6:4}. TV. BBC2, 31 May. 21.30 hrs.
  \tcblower
\begin{Verbatim}
@misc{inn2021huw,
  year = {2021},
  title = {Hurry up and wait},
  howpublished = {\emph{Inside no.9}, \emph{Episode 6:4}. TV. BBC2, 31 May.
    21.30 hrs}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{rsfo2006ep5}
  Rick Stein's French odyssey: Episode 5, 2006. TV. BBC2, 23 August. 20.30 hrs.
  \tcblower
\begin{Verbatim}
@misc{rsfo2006ep5,
  year = {2006},
  title = {Rick {Stein's} {French} Odyssey: {Episode} 5},
  howpublished = {TV. BBC2, 23 August. 20.30 hrs}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{archers20060823}
  The Archers, 2006. Radio. BBC Radio 4, 23 August. 19.02 hrs.
  \tcblower
\begin{Verbatim}
@misc{archers20060823,
  year = {2006},
  title = {The {Archers}},
  howpublished = {Radio. BBC Radio 4, 23 August. 19.02 hrs}}
\end{Verbatim}
\end{bibexbox}

\begin{info}\item
Internally, \texttt{audio} and \texttt{music} are aliases for \texttt{booklet}.
\end{info}

\begin{bibexbox}<RX>{tkmmm2020ts}
  The secret, 2020. \emph{Tiger king: murder, mayhem and madness}, \emph{Episode 3} [Online]. TV. Available from: Netflix [Accessed 4 May 2021].
  \tcblower
\begin{Verbatim}
@misc{tkmmm2020ts,
  year = {2020},
  title = {The Secret},
  howpublished = {\emph{Tiger king: murder, mayhem and madness}, \emph{Episode 3}
    [Online]. TV},
  note = {Available from: Netflix [Accessed 4 May 2021]}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Music score}

\begin{bibexbox}<RX>{beethoven1950symph1}
  Beethoven, L. van, 1950. \emph{Symphony no.1 in C, Op.21}. Harmondsworth: Penguin.
  \tcblower
\begin{Verbatim}
@book{beethoven1950symph1,
  author = {Ludwig van Beethoven},
  year = {1950},
  title = {Symphony no.1 in {C,} {Op.21}},
  address = {Harmondsworth},
  publisher = {Penguin}}
\end{Verbatim}
\end{bibexbox}

\subsection{Digital media}

\subsubsection*{Website or webpage}

While it is normal when using Bib\TeX\ to use \texttt{misc} for websites,
with this style you should use \texttt{online} (or \texttt{electronic} or \texttt{www}) instead.
Internally these are all aliases for \texttt{manual}.

\begin{bibexbox}<RX>{who2018ttc}
  World Health Organization, 2018. \emph{The top 10 causes of death} [Online]. Geneva: World Health Organization. Available from: \url{https://www.who.int/news-room/fact-sheets/detail/the-top-10-causes-of-death} [Accessed 29 June 2020].
  \tcblower
\begin{Verbatim}
@manual{who2018ttc,
  author = {{World Health Organization}},
  year = {2018},
  title = {The Top 10 Causes of Death},
  titleaddon = {[Online]},
  address = {Geneva},
  organization = {World Health Organization},
  url = {https://www.who.int/news-room/fact-sheets/detail/the-top-10-causes-of-death},
  urldate = {29 June 2020}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{manco2013va}
  Manco, J., 2013. \emph{Vernacular architecture} [Online]. Available from: \url{https://www.buildinghistory.org/style/vernacular.shtml} [Accessed 20 February 2020].
  \tcblower
\begin{Verbatim}
@manual{manco2013va,
  author = {Manco, J.},
  year = {2013},
  title = {Vernacular Architecture},
  titleaddon = {[Online]},
  url = {https://www.buildinghistory.org/style/vernacular.shtml},
  urldate = {20 February 2020}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Social media}

\begin{bibexbox}<RX>{gaiman2021fbp}
  Gaiman, N., 2021. \emph{Facebook post} [Online], 21 April. Available from: \url{https://www.facebook.com/neilgaiman/posts/305187897642814} [Accessed 13 May 2021].
  \tcblower
\begin{Verbatim}
@manual{gaiman2021fbp,
  author = {Gaiman, N.},
  year = {2021},
  title = {Facebook post},
  titleaddon = {[Online]},
  month = {21 April},
  url = {https://www.facebook.com/neilgaiman/posts/305187897642814},
  urldate = {13 May 2021}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{ublib2021tp}
  Library at University of Bath [@bathunilibrary], 2021. \emph{Twitter post} [Online], 10 May. Available from: \url{https://twitter.com/BathUniLibrary/status/1391774402618998795?s=20} [Accessed 12 May 2021].
  \tcblower
\begin{Verbatim}
@manual{ublib2021tp,
  author = {{Library at University of Bath [@bathunilibrary]}},
  year = {2021},
  title = {Twitter post},
  titleaddon = {[Online]},
  month = {10 May},
  url = {https://twitter.com/BathUniLibrary/status/1391774402618998795?s=20},
  urldate = {12 May 2021}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{ublib2021ip}
  University of Bath Library [@unibathlib], 2021. \emph{Instagram post} [Online], 15 March. Available from: \url{https://www.instagram.com/p/CMb5GHjFv9A/?utm_source=ig_web_copy_link} [Accessed 7 May 2021].
  \tcblower
\begin{Verbatim}
@manual{ublib2021ip,
  author = {{University of Bath Library [@unibathlib]}},
  year = {2021},
  title = {Instagram post},
  titleaddon = {[Online]},
  month = {15 March},
  url = {https://www.instagram.com/p/CMb5GHjFv9A/?utm_source=ig_web_copy_link},
  urlyear = {7 May 2021}}
\end{Verbatim}
\end{bibexbox}

\begin{hacks}\item
Unfortunately, the handle will also show up in your citations, e.g.\@
\cite{ublib2021ip}. To avoid this, you could use alternative citation commands:
\begin{tcblisting}{listing side text, lefthand width=.46\linewidth}
University of Bath Library \citeyearpar{ublib2021ip}
\end{tcblisting}
\end{hacks}

\subsubsection*{Email discussion lists (jiscmail\slash listserv etc.)}

\begin{bibexbox}(hacked)<RX>{clark2004euk}
  Clark, T., 5 July 2004. A European UK Libraries Plus? \emph{Lis-link} [Online]. Available from: \url{lis-link@jiscmail.ac.uk} [Accessed 30 July 2004].
  \tcblower
\begin{Verbatim}
@article{clark2004euk,
  author = {Clark, T.},
  year = {5 July 2004},
  title = {A {European} {UK} {Libraries} {Plus}?},
  journal = {Lis-link \textup{[Online]}},
  url = {lis-link@jiscmail.ac.uk},
  urldate = {30 July 2004}}
\end{Verbatim}
\end{bibexbox}

\begin{tips}\item
Use the \texttt{journal} field to specify the mailing list.
\end{tips}

\begin{hacks}\item
You will need to put the full date in the \texttt{year} field;
unfortunately this means you have to put in extra work to show only the year in citations:
\end{hacks}

\begin{tcblisting}{listing side text, lefthand width=.5\linewidth}
\citetext{\citeauthor[2004]{clark2004euk}}
\end{tcblisting}

\subsubsection*{Database}

\begin{bibexbox}<RX>{bvd2008bt}
  Bureau van Dijk, 2008. \emph{BT Group plc company report}. \emph{FAME} [Online]. London: Bureau van Dijk. Available from: \url{http://www.portal.euromonitor.com} [Accessed 6 November 2014].
  \tcblower
\begin{Verbatim}
@manual{bvd2008bt,
  author = {{Bureau van Dijk}},
  year = {2008},
  title = {{BT} {Group} PLC Company Report},
  series = {\emph{FAME} {[Online]}},
  address = {London},
  organization = {Bureau van Dijk},
  url = {http://www.portal.euromonitor.com},
  urldate = {6 November 2014}}
\end{Verbatim}
\end{bibexbox}


\subsubsection*{Dataset}

\begin{bibexbox}<RX>{wilson2013rgc}
  Wilson, D., 2013. \emph{Real geometry and connectedness via triangular description: CAD example bank} [Online]. Bath: University of Bath. Available from: \url{https://doi.org/10.15125/BATH-00069} [Accessed 20 April 2016].
  \tcblower
\begin{Verbatim}
@manual{wilson2013rgc,
  author = {Wilson, D.},
  year = {2013},
  title = {Real Geometry and Connectedness via Triangular Description: {CAD} Example Bank},
  titleaddon = {[Online]},
  address = {Bath},
  organization = {University of Bath},
  doi = {10.15125/BATH-00069},
  urldate = {20 April 2016}}
\end{Verbatim}
\end{bibexbox}

\begin{info}\item
You can use \texttt{dataset} instead of \texttt{online} as an alias for \texttt{manual}.
\end{info}

\subsubsection*{Computer program}

\begin{bibexbox}<RX>{screencasto}
  @screencasto, n.d. \emph{Screencast-O-Matic} (v.2) [computer program]. Available from: \url{https://screencast-o-matic.com/} [Accessed 16 May 2016].
  \tcblower
\begin{Verbatim}
@manual{screencasto,
  author = {@screencasto},
  year = {n.d.},
  title = {{Screencast-O-Matic}},
  titleaddon = {(v.2) [computer program]},
  url = {https://screencast-o-matic.com/},
  urldate = {16 May 2016}}
\end{Verbatim}
\end{bibexbox}

\begin{info}\item
Internally, \texttt{software} is an alias for \texttt{manual}.
\end{info}

\subsection{Works in languages other than English}

\subsubsection*{Work in translation}

\begin{bibexbox}<RX>{aristotle2007ne}
  Aristotle, 2007. \emph{Nicomachean ethics} (W.D. Ross, Trans.). South Dakota: NuVisions.
  \tcblower
\begin{Verbatim}
@book{aristotle2007ne,
  author = {Aristotle},
  year = {2007},
  title = {Nicomachean Ethics},
  titleaddon = {(W.D. Ross, Trans.)},
  address = {South Dakota},
  publisher = {NuVisions}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Work in the Roman alphabet}

\begin{bibexbox}<RX>{esquivel2003cap}
  Esquivel, L., 2003. \emph{Como agua para chocolate} [Like water for chocolate]. Barcelona: Debolsillo.
  \tcblower
\begin{Verbatim}
@book{esquivel2003cap,
  author = {Esquivel, L.},
  year = {2003},
  title = {Como Agua para Chocolate},
  titleaddon = {[Like water for chocolate]},
  address = {Barcelona},
  publisher = {Debolsillo}}
\end{Verbatim}
\end{bibexbox}

\begin{tips}\item
Use the \texttt{titleaddon} field to supply the English translation of the title.
\end{tips}

\begin{bibexbox}<RX>{thurfjell1975vhv}
  Thurfjell, W., 1975. Vart har våran doktor tagit vägen? [Where has our doctor gone?]. \emph{Läkartidningen}, 72, p.789.
  \tcblower
\begin{Verbatim}
@article{thurfjell1975vhv,
  author = {Thurfjell, W.},
  year = {1975},
  title = {Vart har våran doktor tagit vägen?},
  titleaddon = {[Where has our doctor gone?]},
  journal = {Läkartidningen},
  volume = {72},
  pages = {789}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Work in a non-Roman alphabet}

\newcommand*{\noop}[1]{}
\begin{bibexbox}(hacked)<RX>{hua1999qys1}
  Hua, L. 華林甫, 1999. Qingdai yilai Sanxia diqu shuihan zaihai de chubu yanjiu 清代以來三峽地區水旱災害的初步硏 [A preliminary study of floods and droughts in the Three Gorges region since the Qing dynasty]. \emph{Zhongguo shehui kexue \emph{中國社會科學}}, 1, pp.168--79.
  \tcblower
\begin{Verbatim}
@article{hua1999qys1,
  author = {Linfu \noop{h}華林甫 Hua},
  year = {1999},
  title = {Qingdai yilai {Sanxia} diqu shuihan zaihai de chubu yanjiu
    {清代以來三峽地區水旱災害的初步硏}},
  titleaddon = {[A preliminary study of floods and droughts in the {Three} {Gorges} region since
    the {Qing} dynasty]},
  journal = {Zhongguo shehui kexue \emph{中國社會科學}},
  volume = {1},
  pages = {168-79}}
\end{Verbatim}
\end{bibexbox}

\begin{tips}\item
The above example tricks Bib\TeX\ into treating the original rendering of
the author's name as the `von' part of a Roman-alphabet name. This requires the
use of a command that simply gobbles its argument, which you have to define
yourself:

\begin{tcblisting}{listing only}
\newcommand*{\noop}[1]{}
\end{tcblisting}

For the trick to work, the argument you give to \lstinline[style=dtxlatex]|\noop|
must be lowercase, but otherwise it can be anything you like.
\item
If the name is due to appear initial first (e.g.~after `In:'), you can append
the non-Roman characters to the author's surname; to do this, use inverted name
order as you would for English double-barrelled names without hyphens, e.g.\@
\texttt{Hua 華林甫, Linfu}.
\end{tips}

\begin{bibexbox}<RX>{hua1999qys2}
  Hua, L., 1999. Qingdai yilai Sanxia diqu shuihan zaihai de chubu yanjiu [A preliminary study of floods and droughts in the Three Gorges region since the Qing dynasty]. \emph{Zhongguo shehui kexue}, 1, pp.168--79.
  \tcblower
\begin{Verbatim}
@article{hua1999qys2,
  author = {Hua, Linfu},
  year = {1999},
  title = {Qingdai yilai {Sanxia} diqu shuihan zaihai de chubu yanjiu},
  titleaddon = {[A preliminary study of floods and droughts in the {Three} {Gorges} region since
    the {Qing} dynasty]},
  journal = {Zhongguo shehui kexue},
  volume = {1},
  pages = {168-79}}
\end{Verbatim}
\end{bibexbox}

\begin{bibexbox}<RX>{pamporov2006rvb}
  Pamporov, A., 2006. \emph{Romskoto vsekidnevie v Balgariya} [Roma everyday life in Bulgaria]. Veliko Tarnovo: Faber.
  \tcblower
\begin{Verbatim}
@book{pamporov2006rvb,
  author = {Pamporov, A.},
  year = {2006},
  title = {Romskoto vsekidnevie v {Balgariya}},
  titleaddon = {[Roma everyday life in Bulgaria]},
  address = {Veliko Tarnovo},
  publisher = {Faber}}
\end{Verbatim}
\end{bibexbox}

\subsection{Legal or government document: UK parliamentary reports\slash legislation}


\subsubsection*{House of Commons paper}

\begin{tips}\item
Use this form for reports of House of Commons select committees.
\end{tips}

\begin{bibexbox}<RX>{gb.hc2003/04-30}
  Great Britain. Parliament. House of Commons, 2004. \emph{National Savings investment deposits: account 2002--2003}. (HC 2003/04, 30). London: National Audit Office.
  \tcblower
\begin{Verbatim}
@techreport{gb.hc2003/04-30,
  author = {{Great Britain. Parliament. House of Commons}},
  year = {2004},
  title = {National {Savings} Investment Deposits: account 2002--2003},
  address = {London},
  publisher = {National Audit Office},
  type = {{HC}},
  number = {2003/04, 30}}
\end{Verbatim}
\end{bibexbox}


\subsubsection*{House of Lords paper}

\begin{tips}\item
Use this form for reports of House of Lords select committees.
\end{tips}

\begin{bibexbox}<RX>{gb.hl1986/87-66}
  Great Britain. Parliament. House of Lords, 1987. \emph{Social fund (maternity and funeral expenses) bill}. (HL 1986/87, (66)). London: HMSO.
  \tcblower
\begin{Verbatim}
@techreport{gb.hl1986/87-66,
  author = {{Great Britain. Parliament. House of Lords}},
  year = {1987},
  title = {Social Fund (Maternity and Funeral Expenses) Bill},
  address = {London},
  publisher = {HMSO},
  type = {{HL}},
  number = {1986/87, (66)}}
\end{Verbatim}
\end{bibexbox}


\subsubsection*{Command paper}

\begin{bibexbox}<RX>{gb.cm6041}
  Great Britain. Ministry of Defence, 2004. \emph{Delivering security in a changing world: defence white paper}. (Cm. 6041). London: TSO.
  \tcblower
\begin{Verbatim}
@techreport{gb.cm6041,
  author = {{Great Britain. Ministry of Defence}},
  year = {2004},
  title = {Delivering Security in a Changing World{:} Defence White Paper},
  address = {London},
  publisher = {TSO},
  type = {{Cm.}},
  number = {6041}}
\end{Verbatim}
\end{bibexbox}


\subsubsection*{House of Commons\slash House of Lords bill}

\begin{bibexbox}<RX>{gb.bill1987/88-66}
  Great Britain. Parliament. House of Commons, 1988. \emph{Local government finance bill}. (Bills | 1987/88, 66). London: HMSO.
  \tcblower
\begin{Verbatim}
@techreport{gb.bill1987/88-66,
  author = {{Great Britain. Parliament. House of Commons}},
  year = {1988},
  title = {Local Government Finance Bill},
  address = {London},
  publisher = {HMSO},
  type = {{Bills |}},
  number = {1987/88, 66}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Act of Parliament (UK Statutes) before 1963}

\begin{bibexbox}<RX>{gb.wa1735}
  \emph{Witchcraft Act} \emph{1735} (9 Geo.2, c.5).
  \tcblower
\begin{Verbatim}
@book{gb.wa1735,
  key = {Witchcraft Act 1735},
  title = {Witchcraft {Act} 1735},
  titleaddon = {(9 Geo.2, c.5)}}
\end{Verbatim}
\end{bibexbox}

\subsubsection*{Act of Parliament (UK Statutes) 1963 onwards}

\begin{bibexbox}<RX>{gb.pa2014}
  \emph{Pensions Act} \emph{2014}, c.19. London: TSO.
  \tcblower
\begin{Verbatim}
@book{gb.pa2014,
  key = {Pensions Act 2014},
  title = {Pensions {Act} 2014},
  number = {c.19},
  address = {London},
  publisher = {TSO}}
\end{Verbatim}
\end{bibexbox}


\subsubsection*{Statutory instrument}

\begin{bibexbox}<RX>{gb.hmr2012}
  \emph{The Human Medicines Regulations} \emph{2012} [Online], No.1916, United Kingdom: HMSO. Available from: \url{http://www.legislation.gov.uk/uksi/2012/1916/pdfs/uksi_20121916_en.pdf} [Accessed 17 April 2016].
  \tcblower
\begin{Verbatim}
@book{gb.hmr2012,
  title = {The {Human} {Medicines} {Regulations} 2012},
  titleaddon = {[Online]},
  number = {No.1916},
  address = {United Kingdom},
  publisher = {HMSO},
  url = {http://www.legislation.gov.uk/uksi/2012/1916/pdfs/uksi_20121916_en.pdf},
  urldate = {17 April 2016},
  keywords = {uksi}}
\end{Verbatim}
\end{bibexbox}

\begin{tips}\item
Use the \texttt{uksi} keyword to trigger the comma before the publisher.
It should be ignored harmlessly by other styles.
\end{tips}

\subsection{Legal or government document: EU reports\slash legislation}


\subsubsection*{EU publication}

\begin{bibexbox}<RX>{ec2015gra}
  European Commission, 2015. \emph{General report on the activities of the European Union 2014}. Luxembourg: Publications Office of the European Union.
  \tcblower
\begin{Verbatim}
@techreport{ec2015gra,
  author = {{European Commission}},
  year = {2015},
  title = {General Report on the Activities of the {European} {Union} 2014},
  address = {Luxembourg},
  publisher = {Publications Office of the European Union}}
\end{Verbatim}
\end{bibexbox}


\subsubsection*{EU regulation or directive, decision, recommendation or opinion}

\begin{bibexbox}<RX>{eu.dir1984/2003}
  Council Regulation (EC) 1984/2003 of 8 April 2003 introducing a system for the statistical monitoring of trade in bluefin tuna, swordfish and big eye tuna within the Community [2003] \emph{OJ} L295.
  \tcblower
\begin{Verbatim}
@misc{eu.dir1984/2003,
  title = {Council {Regulation} ({EC}) 1984/2003 of 8 {April} 2003 Introducing a System for
    the Statistical Monitoring of Trade in Bluefin Tuna, Swordfish and Big Eye Tuna within
    the {Community}},
  titleaddon = {[2003] \emph{OJ} L295}}
\end{Verbatim}
\end{bibexbox}

\begin{hacks}\item
Use \lstinline[style=dtxlatex]|\defcitealias| to provide a suitable citation string:
\begin{tcblisting}{listing side text, lefthand width=.46\linewidth}
\defcitealias{eu.dir1984/2003}{%
  Council Regulation [EC] 1984/2003}
\citepalias{eu.dir1984/2003}
\end{tcblisting}
\end{hacks}

\subsection{Legal or government document: case reports}

\subsubsection*{Legal case study}

\begin{bibexbox}<RX>{seldon-v-c.w.j2012}
  \emph{Seldon v.~Clarkson Wright \& Jakes}. [2012]. UKSC 16.
  \tcblower
\begin{Verbatim}
@report{seldon-v-c.w.j2012,
  title = {Seldon v.~{Clarkson} {Wright} \& {Jakes}},
  note = {[2012]. UKSC 16}}
\end{Verbatim}
\end{bibexbox}

\begin{info}\item
Generally speaking, the year should be in square brackets if it is essential to the citation
(unless it is a Scottish case, in which case it is printed bare), and in parentheses if it is
not.
\end{info}

\subsubsection*{Judgment of the European Court of Justice}

\begin{bibexbox}<RX>{srl.etal-v-comm2005}
  \emph{Alessandrini Srl and others v.~Commission} (C-295/03 P) [2005] ECR I--5700.
  \tcblower
\begin{Verbatim}
@report{srl.etal-v-comm2005,
  title = {Alessandrini {Srl} and others v.~{Commission}},
  titleaddon = {(C-295/03 P) [2005] ECR I--5700}}
\end{Verbatim}
\end{bibexbox}


\bibliography{bath-bst-v1}
\end{document}
%% 
%% Copyright (C) 2016-2022 by University of Bath
%%
%% End of file `bath-bst-v1.tex'.
